---
title: "bear cam sighting matrix"
author: "Ainsley"
date: "7/6/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Creating a dataset for the matrix of sightings by week

```{r}
library(dplyr)
library(tidyr)

cam_mat <- read.csv("C:/Users/axmac/Desktop/git-general-home/BBearOccuModels2021/bear camera by week matrix.csv")

#abbreviate the headers
ccmat <- cam_mat
colnames(ccmat)[2:11] <- stringr::str_replace(colnames(cam_mat)[2:11], "Week.", "wk") %>%
  stringr::str_sub(1, 3)
#clean up data frame
ccmat <- ccmat[-28,] %>% select(SITE_ID = Site, everything(), - X)

#make site covariate matrix/dataframe
site_covs_data <- read.csv("C:/Users/axmac/Desktop/Bear Kristensen Lab/arcgis_maps/2019_Sampling_Design/all_site_covariates_250m_buffercsv.csv")

#combine datasites but only take those with cameras
sitecov_cams <- left_join(ccmat, site_covs_data, by = "SITE_ID")
```

Now there exists a data set with the sighting's matrix as well as each camera site's covariates (all of them that exist)



Let's format it for unmarked with unmarkedFrameOcc() function
```{r}
y <- sitecov_cams[,2:10]

siteCovs <- sitecov_cams[,11:34]
  
#obsCovs <- 

umframe <- unmarkedFrameOccu(y = y, siteCovs = siteCovs)
summary(umframe)
```
Questions: does the Y's matrix have to be binary? How does the date factor in? Should I scale? probably but for now let's figure out basics

==============================================================
==============================================================

Making models and comparing AIC:
  AIC = an estimator of prediction error
  If a model is more than 2 units lower than another, it is considered a better model. Lower is better.


```{r empty model}
ufme <- occu(formula = ~1 ~1
                      , data = umframe)
ufme
```
```{r full model}
ufmf <- occu(formula = ~. ~.
                      , data = umframe)
ufmf
```

Other combos just to play around but will eventually decide on just a few to look into:
```{r}
ufm2 <- occu(formula = ~1 ~ Conifer.forest...proportion. +
               Agriculture..proportion. +
               Deciduous.forest...proportion.
                      , data = umframe)
ufm2
```

```{r}
ufm3 <- occu(formula = ~1 ~ Conifer.forest...proportion. +
               Agriculture..proportion. +
               Deciduous.forest...proportion. +
               Housing.density..mean.
                      , data = umframe)
ufm3
```


